Independent Component Analysis

### 2022-04-17 paper.tex
more section summaries

\section{Mathematical Formulation}
1) Optimizing Kurtosis
2) Minimizing mutual information
3) Maximum likelihood estimation

\section{Algorithms and Applications}
1) projection pursuit (kurtotis)
2) FastICA (minimizing mutual information

>>>>

\section{Mathematical Formulation}
0) Proof that gaussian signals cannot be separated (Kannan)
1) Optimizing Kurtosis (Kannan)
2) Minimizing mutual information (Mick)
3) Maximum likelihood estimation (Mick)

\section{Algorithms and Applications}
1) projection pursuit (kurtotis) (Kannan)
2) FastICA (minimizing mutual information (Mick)
